First steps with PyEMMA : v\versionnumber

### 2018-07-06 manuscript.tex
adding first two figures and draft pdf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Learning PyEMMA : v\versionnumber}

\author[1\authfn{1}*]{AUTH0}
\author[1\authfn{1}*]{Martin K. Scherer}
\author[1*]{AUTH2}
\affil[1]{AFFILIATION}

\corr{auth0@email}{A0}
\corr{m.scherer@fu-berlin.de}{A1}
\corr{auth2@email}{A2}

@@

\blurb{This LiveCoMS document is maintained online on GitHub at \githubrepository; to provide feedback, suggestions, or help improve it, 
please visit the GitHub repository and participate via the issue tracker.}

@@

\begin{abstract}
This tutorial provides an introduction to the PyEMMA project. Using Jupyter notebooks and accompanying screencasts, 
we will guide you through the basic functionality as well as the more common advanced mechanisms. 
Short exercises to self check your learning progress and a notebook on troubleshooting complete this basic introduction.
\end{abstract}

@@

@@

@@

All notebooks are available on \githubrepository where you also might find additional materials and installation instructions.

\section{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
For a more detailed description of author contributions, see the GitHub issue tracking and changelog at \githubrepository.

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
For a more detailed description of contributions from the community and others, see the GitHub issue tracking and changelog at \githubrepository.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{First steps with PyEMMA : v\versionnumber}

\author[1\authfn{1}*]{Christoph Wehmeyer}
\author[1\authfn{1}*]{Martin K. Scherer}
\author[1*]{Tim Hempel}
\author[1*]{Simon Olsson}
\author[1*]{Frank Noé}
\affil[1]{Department of Mathematics and Computer Science, Freie Universität Berlin, Arnimallee 6, 14195 Berlin, Germany}

\corr{christoph.wehmeyer@fu-berlin.de}{CW}
\corr{m.scherer@fu-berlin.de}{MS}
\corr{tim.hempel@fu-berlin.de}{TH}
\corr{simon.olsson@fu-berlin.de}{SO}
\corr{frank.noe@fu-berlin.de}{FN}

@@

\blurb{This LiveCoMS document is maintained online on GitHub at \githubrepository{}; to provide feedback, suggestions, or help improve it, 
please visit the GitHub repository and participate via the issue tracker.}

@@

\begin{abstract}
This tutorial provides an introduction to the PyEMMA project. Using Jupyter notebooks, we will guide you through the basic functionality as well as the more common advanced mechanisms. Short exercises to self check your learning progress and a notebook on troubleshooting complete this basic introduction.
\end{abstract}

@@

\begin{figure}
\includegraphics{figure_1}
\caption{Exemplary analysis of a pentapeptide's backbone conformational dynamics: (a) The VAMP2 score indicates which of the tested featurization contains the most kinetic variance. (b) The first two independent components of a TICA projection at lag time $\tau=0.5$ ns show rare transition events. (c) Projection of the sample distribution and 200 $k$-means cluster centers onto the first two independent TICA components. (d) The convergence behavior of the first four implied timescales indicates that a lag time of $\tau=0.5$ ns is suitable for estimating an MSM; the shaded areas indicate $95\%$ confidence intervals.}
\label{fig:io-to-its}
\end{figure}

Figure~\ref{fig:io-to-its}

@@

\begin{figure}
\includegraphics{figure_2}
\caption{A Chapman-Kolmogorov test shows that an MSM estimated at lag time $\tau=0.5$ ns accurately predicts the kinetic behavior on longer timescales; the shaded areas indicate $95\%$ confidence intervals.}
\label{fig:ck}
\end{figure}

Figure~\ref{fig:ck}

@@

All notebooks are available on \githubrepository{} where you also might find additional materials and installation instructions.

\section{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
For a more detailed description of author contributions, see the GitHub issue tracking and changelog at \githubrepository{}.

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
For a more detailed description of contributions from the community and others, see the GitHub issue tracking and changelog at \githubrepository{}.
